% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
% \usepackage{NotoSansSC_external}
% \usepackage{NotoSerifCJKsc_external}
% \usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Chenkai (Nicholas) Wang}

\basicInfo{
  \email{me@nicho1as.wang} \textperiodcentered\
  \phone{+1 (256)414-2048}
}

\LARGE
Thank you for the opportunity to apply at your company. After reviewing your job description, it’s clear that you’re looking for a candidate that is extremely familiar with the responsibilities associated with the role, and can perform them confidently. Given these requirements, I am certain that I have the necessary skills to successfully do the job adeptly and perform above expectations.
\newline
\newline
I am currently a college student with 3.5 GPA, B.S. in GIS and minor in Computer Science from University of Illinois Urbana-Champaign, and I am expected to graduate on May, 2021. During the course of my academic career, I also managed to accrue nearly 3 years of work experience. I had been working for Hefei Tuocheng Mould Technology Co., Ltd in a embedded software developer role in my free time, mostly summer and winters, where I performed STM32 and AVR-based embedded systems' PCB design, firmware design based on C and C++ language, including projects with closed-loop motion control, a.k.a PID control. Plus, I've contributed to open source projects based on C and Golang, mostly networking utilities and proxies. In both my academic and professional life, I have been consistently praised as efficient by my professors and peers. Whether working on academic, extracurricular, or professional projects, I apply proven teamwork, service and technical skills, which I hope to leverage into the Software Developer role at your company.
\newline
\newline
After reviewing my resume, I hope you will agree that I am the type of competent and competitive candidate you are looking for. I look forward to elaborating on how my specific skills and abilities will benefit your organization.
\newline
\newline
Thank you for your consideration, and I look forward to hearing from you soon.


\end{document}
